Molecular transport in human pial perivasculature

### 2024-11-18 paper/supplementary_main.tex
Updates from Overleaf

Further assuming unsteady dispersion, we follow Sharp et al \cite{keith2019dispersion} and calculate the enhancement factor $R$ from the non-dimensionalized pressure gradient $dP=\frac{|\nabla p|}{\omega \mu / h}$ as $R\approx dP^2 / \alpha^3$. Combining the computed pressure gradient with this scaling law yields a pointwise approximation of the dispersion factor. Finally, we account for the non-local nature of the dispersion mechanism by applying a smoothing technique to obtain a spatially varying, but locally averaged diffusion enhancement factor $R$ (see the visualization in \cref{fig:visualize_R} and \cref{sec:dispersion_details} for additional details).

>>>>

Further assuming unsteady dispersion, we follow Sharp et al \cite{keith2019dispersion} and calculate the enhancement factor $R$ from the non-dimensionalized pressure gradient $dP=\frac{|\nabla p|}{\omega \mu / h}$ \rami{Can we refer to the exact equation here from Sharp et al ? i find that they write $P = (\partial \tilde p / \partial \tilde x) / (\rho \omega \mu_e/h)$ ... so i am a bit confused
}as $R\approx dP^2 / \alpha^3$. Combining the computed pressure gradient with this scaling law yields a pointwise approximation of the dispersion factor. Finally, we account for the non-local nature of the dispersion mechanism by applying a smoothing technique to obtain a spatially varying, but locally averaged diffusion enhancement factor $R$ (see the visualization in \cref{fig:visualize_R} and \cref{sec:dispersion_details} for additional details).
